\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Siemens Healthineers}{Bangalore, India}
    {Software Engineer 1}{July 2023 -- Present}
    \resumeItemListStart
      \resumeItem{\textbf{Architected and optimized high-throughput distributed services} (C++/Go) handling \textbf{10+ TBs} of streaming data daily; engineered custom memory allocators and lock-free structures to reduce latency by \textbf{40\%}.}
      \resumeItem{\textbf{Implemented robust fault-tolerance mechanisms} including circuit breakers and exponential backoff, ensuring \textbf{99.99\%} system availability and eliminating data loss during peak loads.}
      \resumeItem{\textbf{Designed scalable ingestion pipelines} and storage layers; optimized I/O patterns to increase throughput by \textbf{3x} and reduced storage costs by \textbf{25\%} via efficient data validation.}
      \resumeItem{\textbf{Enhanced system observability} with distributed tracing and structured logging; developed internal CLI tools that automated recovery, reducing MTTR by \textbf{50\%} and boosting velocity.}
      \resumeItem{\textbf{Orchestrated containerized microservices deployments} on Linux/Azure, accelerating release cycles by \textbf{20\%} via Agile delivery.}
    \resumeItemListEnd

  \resumeSubheading
    {Siemens Healthineers}{Bangalore, India}
    {Software Engineer Intern}{February 2023 -- July 2023}
    \resumeItemListStart
      \resumeItem{Implemented \textbf{REST APIs} and data models in C\#; contributed to ingestion/validation modules and unit/integration tests.}
      \resumeItem{Automated developer workflows and CI tasks; participated in \textbf{synchronous code/design reviews}, improving maintainability and on‑time delivery; achieved \textbf{60\%} process time savings.}
    \resumeItemListEnd

  \resumeSubheading
    {Beneath-a-Tree}{India}
    {Techno-Managerial STEM Internship}{February 2022 -- March 2022}
    \resumeItemListStart
      \resumeItem{As a team of 4 STEM Trainers in Rural Gujarat for the STEM for Girls initiative, sparking interest in science and research. Planned events, communicated interculturally, and managed resources, logistics and execution.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
